A seamless, client-centric programming model for type safe web applications

### 2014-03-01 paper.tex
Replace monolithic by words without accidental negative connotations.

Development of web applications is no task for the faint of heart.
The conventional method involves splitting your program into two logical parts,
writing the one in Javascript, which is notorious even among its proponents for
being wonky and error-prone, and the other in any compiled or
server-interpreted language. Then, two are glued together using whichever
home-grown network protocol seems to fit the application. However, most web
applications are conceptually monolithic entities, making this forced split an
undesirable hindrance which introduces new possibilities for defects, adds
development overhead and prevents code reuse.

@@

There are many conveivable improvements to the mainstream web development model
described in the previous section. We propose an alternative programming model
based on Haskell, in which web applications are written as monolithic entities
rather than as two independent parts that just so happen to talk to each other.

@@

\begin{itemize}
  \item The language must provide a static type system, since one of our
        primary concerns is to reduce defect rates through static typing of
        the client-server communication channel.
  \item The language must be compilable to both Javascript and a format
        suitable for server-side execution as we want our web applications
        to be written as a single, monolithic program.
  \item We want the language to provide decent support for a monadic
        programming style, as we our abstractions for cooperative multitasking
        and synchronous client-server communication are neatly expressible in
        this style.
\end{itemize}

>>>>

Development of web applications is no task for the faint of heart.
The conventional method involves splitting your program into two logical parts,
writing the one in Javascript, which is notorious even among its proponents for
being wonky and error-prone, and the other in any compiled or
server-interpreted language. Then, two are glued together using whichever
home-grown network protocol seems to fit the application. However, most web
applications are conceptually single entities, making this forced split an
undesirable hindrance which introduces new possibilities for defects, adds
development overhead and prevents code reuse.

@@

There are many conveivable improvements to the mainstream web development model
described in the previous section. We propose an alternative programming model
based on Haskell, in which web applications are written as a single program
rather than as two independent parts that just so happen to talk to each other.

@@

\begin{itemize}
  \item The language must provide a static type system, since one of our
        primary concerns is to reduce defect rates through static typing of
        the client-server communication channel.
  \item The language must be compilable to both Javascript and a format
        suitable for server-side execution as we want our web applications
        to be written and compiled as a single program.
  \item We want the language to provide decent support for a monadic
        programming style, as we our abstractions for cooperative multitasking
        and synchronous client-server communication are neatly expressible in
        this style.
\end{itemize}
